---
title: "Single Molecule Localization in R (SMolR)"
author: "Maarten Paul (m.w.paul@erasmusmc.nl)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SMolR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r,cache=TRUE}
library(SMolR)
```

The SMolR package consists of a set of functions dedicated to quantitive analysis of Single Molecule Localization data in R.

- Importing and organizing large single molecule localization data sets
- Visualize super resolution localization data
- High-thoughput analysis of large 



## Import of localization data

Using `SMOLR_IMPORT` different types of data can be imported into R from a folder. The localizations from different ROIs or images are sorted in a `list` of `data.frame`'s. Different `profiles` are available to load different types of data.

```{r}
SMOLR_IMPORT(folder="../loc",profile = "roiloc")
SMOLR_LOAD(folder="../loc")
```

Example of localizations `data.frame`

```{r, echo=TRUE, results='asis'}
knitr::kable(head(localizations[[1]], 10))
```


## Visualization

```{r, fig.show='hold',fig.width=8}
img <- SMOLR(smolrdata)
plot(img)
```

```{r, fig.show='hold'}
plot(img,rgb=TRUE)
```

```{r, fig.show='hold'}
plot(SMOLR(subset(smolrdata,Channel==1)))
```

## Clustering